---
title: "Coral_Protein_Outliers_Removed"
author: "Rafael Solorzano"
date: "5/28/2021"
output: word_document
---


```{r Calling in packages, include=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(dplyr)
library(janitor)
library(hrbrthemes)
library(viridis)
library(ggpubr)
library(rstatix)
```

```{r Reading in excel files, include=FALSE}
coral_master_file <- read_excel("~/Desktop/Protein Data/coral_master_file.xlsx")

Protein_conc_host_all<- read_excel("~/Desktop/Protein_conc_host_all.xlsx")

Zoox_protein_conc_all <- read_excel("~/Desktop/Zoox_protein_conc_all.xlsx")

```


# Making a Master Data Dheet

## I figured out a trick to merge the protein data to their respective rows in the master sheet, but then I could not figure out how to work with that giant sheet when making the graphs. I was not too sure how to work with the empty rows or assign them values, so instead I stuck with this version. This version saw all empty rows corresponding to host & symbiont get elimnated, since the values in the holobiont rows should correspond to the empty rows below (as seen in master sheet).

## Then I omitted the "fraction" column because I decided they were not too necessary since the values present on the master would correspond with either host, holobiont, or symbiont. 

## Once I had the master sheet cleaned up, I could then merge relevant host & symbiont protein data, by their ID #.  


```{r}
#remove columns with all NA's 
coral_master_file_1 <- janitor::remove_empty(coral_master_file, which = "cols")
#Remove rows with NA's so we are just left with holobiont data, which matches the other two fractions 
coral_master_file_2 <- na.omit(coral_master_file_1)
#I omitted the fraction column to work with a single id # which is matched with data that is identical for all three fractions 
coral_master_file_2$fraction <- NULL
```

***

# Host & Zoox: Creating Columns of Protein Normalized to Surface Area

## I created new merged (protein + master) data sheets for each host & zoox data frame, which I ended up merging together into "merged_host_et_zoox" which contains the cleaned up master, merged to the surface area normalized host & zoox protein data. 
```{r}
## Protein per coral for host
#merge "vol_add_brush" from the master file to the host data 
#now the master & host data are combined with all like columns plus the additional columns
merged_host <- merge(Protein_conc_host_all,coral_master_file_2)
# I want to multiply proteins_host (mg/mL) * vol_add_brush (mL) = proteins_host (mg) 
merged_host$protein_sa_norm_host <- merged_host$"proteins_host (mg/ml)" * merged_host$vol_add_brush
#Now I want to calculate the normalized protein per coral (host): proteins_host (mg) / sa = surface area normalized protein 
merged_host$protein_sa_norm_host <- merged_host$"protein_sa_norm_host" / merged_host$sa 

## Protein per coral for zoox
#remove last column which has mostly NA's with only a couple comments
Zoox_protein_conc_all$"...8" <- NULL
#master & zoox data are combined with all like columns plus the additional columns
merged_zoox <- merge(Zoox_protein_conc_all,coral_master_file_2)
#I want to calculate the amount of Zoox protein in mg: "proteins_zoox (mg/mL) * vol_add_brush (mL) = zoox protein (mg) 
merged_zoox$protein_sa_norm_zoox <- merged_zoox$"proteins_zoox (mg/ml)" * merged_zoox$vol_add_brush
# I want to normalize the protein for the zoox to surface area: zoox protein (mg) / sa
merged_zoox$protein_sa_norm_zoox <- merged_zoox$"protein_sa_norm_zoox" / merged_zoox$sa 

## merging the merged host & zoox data together 
merged_host_et_zoox <- merge(merged_host,merged_zoox)
```

***

# Symbiont Count Normalization 

*** 
# Normalizing Host Protein to Big symbiont Count: 
## The SC normalized protein units are in mg, but it yielded very small numbers: so I wanted to convert the units to nanograms (ng) by multipluying the (mg/SC) value by 10^6. 
```{r}
#Adding a column of Host protein normalized to big symbiont count (BSC) 
  #First I multiply: "proteins_host (mg/mL) * vol_add_brush (mL) = proteins_host (mg) 
merged_host_et_zoox$protein_BSC_norm_host <- merged_host_et_zoox$"proteins_host (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the big symbiont count (BSC): proteins_host (mg) / big_symbiont_count
      # However, the BSC column needs to be converted from character to numeric 
merged_host_et_zoox$big_symbiont_count <- as.numeric(merged_host_et_zoox$big_symbiont_count)
      # Now I can finally continue to normalize to the BSC 
merged_host_et_zoox$protein_BSC_norm_host <- merged_host_et_zoox$protein_BSC_norm_host  / merged_host_et_zoox$big_symbiont_count 


# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_BSC_norm_host <- merged_host_et_zoox$protein_BSC_norm_host * (1e+06)
```

***
#Normalizing Host Protein to Small Symbiont Count: 
## Converting mg/SC * 1e+06 --> ng/SC
```{r}
#Adding a column of Host protein normalized to small symbiont count (SSC) 
  #First I multiply: "proteins_host (mg/mL) * vol_add_brush (mL) = proteins_host(mg) 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$"proteins_host (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the small symbiont count (SSC): proteins_host (mg) / small_symbiont_count
      # However, the SSC column needs to be converted from character to numeric 
merged_host_et_zoox$small_symbiont_count <- as.numeric(merged_host_et_zoox$small_symbiont_count)
      # Now I can finally continue to normalize to the SSC 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$protein_SSC_norm_host / merged_host_et_zoox$small_symbiont_count


# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$protein_SSC_norm_host * (1e+06)
```

***
#Normalizing Zoox Protein to Big Symbiont Count: 
## Converting mg/SC * 1e+06 --> ng/SC
```{r}
#Adding a column of Zoox protein normalized to big symbiont count (BSC) 
  #First I multiply: "proteins_zoox (mg/mL) * vol_add_brush (mL) = proteins_zoox(mg) 
merged_host_et_zoox$protein_BSC_norm_zoox <- merged_host_et_zoox$"proteins_zoox (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the big symbiont count (BSC): proteins_zoox (mg) / big_symbiont_count
merged_host_et_zoox$protein_BSC_norm_zoox<- merged_host_et_zoox$protein_BSC_norm_zoox / merged_host_et_zoox$big_symbiont_count

# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_BSC_norm_zoox <- merged_host_et_zoox$protein_BSC_norm_zoox * (1e+06)
```

***
#Normalizing Zoox Protein to Small Symbiont Count: 
## Converting mg/SC * 1e+06 --> ng/SC
```{r}
#Adding a column of Zoox protein normalized to small symbiont count (SSC) 
  #First I multiply: "proteins_zoox (mg/mL) * vol_add_brush (mL) = proteins_zoox(mg) 
merged_host_et_zoox$protein_SSC_norm_zoox <- merged_host_et_zoox$"proteins_zoox (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the small symbiont count (SSC): proteins_zoox (mg) / small_symbiont_count
merged_host_et_zoox$protein_SSC_norm_zoox<- merged_host_et_zoox$protein_SSC_norm_zoox / merged_host_et_zoox$small_symbiont_count

# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_SSC_norm_zoox <- merged_host_et_zoox$protein_SSC_norm_zoox * (1e+06)
```

*** 

## By determining the IQR for each surface area normalized host & zoox protein data, 

## One method that I had in mind was that I wanted to determine outliers from the entire columns of normalized host & zoox respectively.I was not sure if that was accurate becuase I figured that since the feeding conditions were causing the differences in [protein], then I would need to eliminate outliers from each group instead. 
## The best analogy that I thought this was like would be heghts of adults and children -- whose outliers would need to be determined in their own respective groups, rather than all lumped together. 

*** 

# Eliminating outliers from big symbiont count normalized host protein 

```{r}
#find Q1, Q3, and interquartile range for values in column: Host protein (BSC normalized) 
Q1_host_BSC <- quantile(merged_host_et_zoox$protein_BSC_norm_host, .25, na.rm = TRUE)
Q3_host_BSC <- quantile(merged_host_et_zoox$protein_BSC_norm_host, .75, na.rm = TRUE)
IQR_host_BSC <- IQR(merged_host_et_zoox$protein_BSC_norm_host, na.rm = TRUE)
#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
protein_BSC_norm_host <- subset(merged_host_et_zoox, merged_host_et_zoox$protein_BSC_norm_host> (Q1_host_BSC - 1.5*IQR_host_BSC) & merged_host_et_zoox$protein_BSC_norm_host< (Q3_host_BSC + 1.5*IQR_host_BSC))
#view row and column count of new data frame
dim(protein_BSC_norm_host) 

merged_host_et_zoox <- data.frame(protein_SSC_norm_host)

```


# Eliminating outliers from big symbiont count normalized Zoox protein 
```{r}
#find Q1, Q3, and interquartile range for values in column: Zoox protein (BSC normalized) 
Q1_zoox_BSC <- quantile(merged_host_et_zoox$protein_BSC_norm_zoox, .25, na.rm = TRUE)
Q3_zoox_BSC <- quantile(merged_host_et_zoox$protein_BSC_norm_zoox, .75, na.rm = TRUE)
IQR_zoox_BSC <- IQR(merged_host_et_zoox$protein_BSC_norm_zoox, na.rm = TRUE)
#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
protein_BSC_norm_zoox <- subset(merged_host_et_zoox, merged_host_et_zoox$protein_BSC_norm_zoox> (Q1_zoox_BSC - 1.5*IQR_zoox_BSC) & merged_host_et_zoox$protein_BSC_norm_zoox< (Q3_zoox_BSC + 1.5*IQR_zoox_BSC))
#view row and column count of new data frame
dim(protein_BSC_norm_zoox) 
```


# Eliminating outliers from small symbiont count normalized Host protein 
```{r}
#find Q1, Q3, and interquartile range for values in column: Host protein (SSC normalized) 
Q1_host_SSC <- quantile(merged_host_et_zoox$protein_SSC_norm_host, .25, na.rm = TRUE)
Q3_host_SSC <- quantile(merged_host_et_zoox$protein_SSC_norm_host, .75, na.rm = TRUE)
IQR_host_SSC <- IQR(merged_host_et_zoox$protein_SSC_norm_host, na.rm = TRUE)
#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
protein_SSC_norm_host <- subset(merged_host_et_zoox, merged_host_et_zoox$protein_SSC_norm_host> (Q1_host_SSC - 1.5*IQR_host_SSC) & merged_host_et_zoox$protein_SSC_norm_host< (Q3_host_SSC + 1.5*IQR_host_SSC)) 
#view row and column count of new data frame
dim(protein_SSC_norm_host) 
```


# Eliminating outliers from small symbiont count normalized Zoox protein 
```{r}
#find Q1, Q3, and interquartile range for values in column: Zoox protein (SSC normalized) 
Q1_zoox_SSC <- quantile(merged_host_et_zoox$protein_SSC_norm_zoox, .25, na.rm = TRUE)
Q3_zoox_SSC <- quantile(merged_host_et_zoox$protein_SSC_norm_zoox, .75, na.rm = TRUE)
IQR_zoox_SSC <- IQR(merged_host_et_zoox$protein_SSC_norm_zoox, na.rm = TRUE)
#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
protein_SSC_norm_zoox <- subset(merged_host_et_zoox, merged_host_et_zoox$protein_SSC_norm_zoox> (Q1_zoox_SSC - 1.5*IQR_zoox_SSC) & merged_host_et_zoox$protein_SSC_norm_zoox< (Q3_zoox_SSC + 1.5*IQR_zoox_SSC))
#view row and column count of new data frame
dim(protein_SSC_norm_zoox) 
```


*** 

### Graphing: Big Symbiont Count Normalized Host Protein  vs _____

## BSC Host protein vs treatments 
```{r}
#15 Protein per coral of host vs treatments 
gg_base_15 <- ggplot(data = merged_host_et_zoox, aes(x = treatment, y = protein_BSC_norm_host, group = treatment))
violin_15 <- gg_base_15 + geom_violin()
violin_15 + geom_boxplot(width = 0.1) + labs(title = "Host BSC norm protein by treatment") + ylim(0,75) +ylab("Host: ng protein/BSC")
```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(treatment) %>%
  get_summary_stats(protein_BSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "treatment", y = "protein_BSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(treatment) %>%
  identify_outliers(protein_BSC_norm_host) 

# Check Normailty: Build the linear model
model_5  <- lm(protein_BSC_norm_host ~ treatment, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_5))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_5))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(treatment) %>%
  shapiro_test(protein_BSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_host", facet.by = "treatment")

# Homogenietey of variance assumption 
plot(model_5, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_host ~ treatment)
res.aov

```



## BSC Host Protein vs Colony 
```{r}
#16 Protein per coral of Host vs colony 
gg_base_16 <- ggplot(data = merged_host_et_zoox, aes(x = colony, y = protein_BSC_norm_host, group = colony))
violin_16 <- gg_base_16 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_16 + geom_boxplot(width = 0.1) + labs(title = "Host BSC norm protein by colony") + ylim(0,70) +ylab("Host: ng protein/BSC")

```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(colony) %>%
  get_summary_stats(protein_BSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "colony", y = "protein_BSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(colony) %>%
  identify_outliers(protein_BSC_norm_host) 

# Check Normailty: Build the linear model
model_1  <- lm(protein_BSC_norm_host ~ colony, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_1))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_1))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(colony) %>%
  shapiro_test(protein_BSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_host", facet.by = "colony")

# Homogenietey of variance assumption 
plot(model_1, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_host ~ colony)
res.aov

```





## BSC Host Protein vs Tank 
```{r}
#17 protein per coral of Host vs tank 
gg_base_17 <- ggplot(data = merged_host_et_zoox, aes(x = tank, y = protein_BSC_norm_host, group = tank))
violin_17 <- gg_base_17 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_17 + geom_boxplot(width = 0.1) + labs(title = "Host BSC norm protein by tank") + ylim(0,75) +ylab("Host: ng protein/BSC")

```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(tank) %>%
  get_summary_stats(protein_BSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "tank", y = "protein_BSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(tank) %>%
  identify_outliers(protein_BSC_norm_host) 

# Check Normailty: Build the linear model
model_9  <- lm(protein_BSC_norm_host ~ tank, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_9))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_9))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(tank) %>%
  shapiro_test(protein_BSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_host", facet.by = "tank")

# Homogenietey of variance assumption 
plot(model_9, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_host ~ tank)
res.aov

```






*** 

#Normalizing Host Protein to Small Symbiont Count: 

## Converting mg/SC * 1e+06 --> ng/SC

```{r}
#Adding a column of Host protein normalized to small symbiont count (SSC) 
  #First I multiply: "proteins_host (mg/mL) * vol_add_brush (mL) = proteins_host(mg) 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$"proteins_host (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the small symbiont count (SSC): proteins_host (mg) / small_symbiont_count
      # However, the SSC column needs to be converted from character to numeric 
merged_host_et_zoox$small_symbiont_count <- as.numeric(merged_host_et_zoox$small_symbiont_count)
      # Now I can finally continue to normalize to the SSC 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$protein_SSC_norm_host / merged_host_et_zoox$small_symbiont_count


# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_SSC_norm_host <- merged_host_et_zoox$protein_SSC_norm_host * (1e+06)
```


### Graphing: Small Symbiont Count Normalized Host Protein  vs _____

## SSC Host protein vs treatments 
```{r}
#18 Protein per coral of host vs treatments 
gg_base_18 <- ggplot(data = merged_host_et_zoox, aes(x = treatment, y = protein_SSC_norm_host, group = treatment))
violin_18 <- gg_base_18 + geom_violin()
violin_18 + geom_boxplot(width = 0.1) + labs(title = "Host SSC norm protein by treatment") + ylim(0,300) +ylab("Host: ng protein/SSC")
```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(treatment) %>%
  get_summary_stats(protein_SSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "treatment", y = "protein_SSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(treatment) %>%
  identify_outliers(protein_SSC_norm_host) 

# Check Normailty: Build the linear model
model_6  <- lm(protein_SSC_norm_host ~ treatment, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_6))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_6))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(treatment) %>%
  shapiro_test(protein_SSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_host", facet.by = "treatment")

# Homogenietey of variance assumption 
plot(model_6, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_host ~ treatment)
res.aov

```



## SSC Host Protein vs Colony 
```{r}
#19 Protein per coral of Host vs colony 
gg_base_19 <- ggplot(data = merged_host_et_zoox, aes(x = colony, y = protein_SSC_norm_host, group = colony))
violin_19 <- gg_base_19 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_19 + geom_boxplot(width = 0.1) + labs(title = "Host SSC norm protein by colony") + ylim(0,800) +ylab("Host: ng protein/SSC")
```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(colony) %>%
  get_summary_stats(protein_SSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "colony", y = "protein_SSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(colony) %>%
  identify_outliers(protein_SSC_norm_host) 

# Check Normailty: Build the linear model
model_2  <- lm(protein_SSC_norm_host ~ colony, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_2))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_2))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(colony) %>%
  shapiro_test(protein_SSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_host", facet.by = "colony")

# Homogenietey of variance assumption 
plot(model_2, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_host ~ colony)
res.aov

```





## SSC Host Protein vs Tank 
```{r}
#20 protein per coral of Host vs tank 
gg_base_20 <- ggplot(data = merged_host_et_zoox, aes(x = tank, y = protein_SSC_norm_host, group = tank))
violin_20 <- gg_base_20 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_20 + geom_boxplot(width = 0.1) + labs(title = "Host SSC norm protein by tank") + ylim(0,300) +ylab("Host: ng protein/SSC")

```
```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(tank) %>%
  get_summary_stats(protein_SSC_norm_host, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "tank", y = "protein_SSC_norm_host")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(tank) %>%
  identify_outliers(protein_SSC_norm_host) 

# Check Normailty: Build the linear model
model_10  <- lm(protein_SSC_norm_host ~ tank, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_10))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_10))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(tank) %>%
  shapiro_test(protein_SSC_norm_host) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_host", facet.by = "tank")

# Homogenietey of variance assumption 
plot(model_10, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_host ~ tank)
res.aov

```

*** 


#Normalizing Zoox Protein to Big Symbiont Count: 

## Converting mg/SC * 1e+06 --> ng/SC

```{r}
#Adding a column of Zoox protein normalized to big symbiont count (BSC) 
  #First I multiply: "proteins_zoox (mg/mL) * vol_add_brush (mL) = proteins_zoox(mg) 
merged_host_et_zoox$protein_BSC_norm_zoox <- merged_host_et_zoox$"proteins_zoox (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the big symbiont count (BSC): proteins_zoox (mg) / big_symbiont_count
merged_host_et_zoox$protein_BSC_norm_zoox<- merged_host_et_zoox$protein_BSC_norm_zoox / merged_host_et_zoox$big_symbiont_count

# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_BSC_norm_zoox <- merged_host_et_zoox$protein_BSC_norm_zoox * (1e+06)
```

### Graphing: Big Symbiont Count Normalized Zoox Protein  vs _____

## BSC Zoox protein vs treatments 
```{r}
#21 Protein per coral of zoox vs treatments 
gg_base_21 <- ggplot(data = merged_host_et_zoox, aes(x = treatment, y = protein_BSC_norm_zoox, group = treatment))
violin_21 <- gg_base_21 + geom_violin()
violin_21 + geom_boxplot(width = 0.1) + labs(title = "Zoox BSC norm protein by treatment")  +ylab("Zoox: ng protein/BSC")


```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(treatment) %>%
  get_summary_stats(protein_BSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "treatment", y = "protein_BSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(treatment) %>%
  identify_outliers(protein_BSC_norm_zoox) 

# Check Normailty: Build the linear model
model_7  <- lm(protein_BSC_norm_zoox ~ treatment, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_7))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_7))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(treatment) %>%
  shapiro_test(protein_BSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_zoox", facet.by = "treatment")

# Homogenietey of variance assumption 
plot(model_7, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_zoox ~ treatment)
res.aov

```



## BSC Zoox Protein vs Colony 
```{r}
#22 Protein per coral of Zoox vs colony 
gg_base_22 <- ggplot(data = merged_host_et_zoox, aes(x = colony, y = protein_BSC_norm_zoox, group = colony))
violin_22 <- gg_base_22 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_22 + geom_boxplot(width = 0.1) + labs(title = "Zoox BSC norm protein by colony") + ylab("Zoox: ng protein/BSC")
```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(colony) %>%
  get_summary_stats(protein_BSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "colony", y = "protein_BSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(colony) %>%
  identify_outliers(protein_BSC_norm_zoox) 

# Check Normailty: Build the linear model
model_3  <- lm(protein_BSC_norm_zoox ~ colony, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_3))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_3))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(colony) %>%
  shapiro_test(protein_BSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_zoox", facet.by = "colony")

# Homogenietey of variance assumption 
plot(model_3, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_zoox ~ colony)
res.aov

```



## BSC Zoox Protein vs Tank 
```{r}
#23 protein per coral of Zoox vs tank 
gg_base_23 <- ggplot(data = merged_host_et_zoox, aes(x = tank, y = protein_BSC_norm_zoox, group = tank))
violin_23 <- gg_base_23 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_23 + geom_boxplot(width = 0.1) + labs(title = "Zoox BSC norm protein by tank") + ylab("Zoox: ng protein/BSC")

```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(tank) %>%
  get_summary_stats(protein_BSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "tank", y = "protein_BSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(tank) %>%
  identify_outliers(protein_BSC_norm_zoox) 

# Check Normailty: Build the linear model
model_11  <- lm(protein_BSC_norm_zoox ~ tank, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_11))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_11))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(tank) %>%
  shapiro_test(protein_BSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_BSC_norm_zoox", facet.by = "tank")

# Homogenietey of variance assumption 
plot(model_11, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_BSC_norm_zoox ~ tank)
res.aov

```

*** 

#Normalizing Zoox Protein to Small Symbiont Count: 

## Converting mg/SC * 1e+06 --> ng/SC

```{r}
#Adding a column of Zoox protein normalized to small symbiont count (SSC) 
  #First I multiply: "proteins_zoox (mg/mL) * vol_add_brush (mL) = proteins_zoox(mg) 
merged_host_et_zoox$protein_SSC_norm_zoox <- merged_host_et_zoox$"proteins_zoox (mg/ml)" * merged_host_et_zoox$vol_add_brush
  #Then I want to normalize to the small symbiont count (SSC): proteins_zoox (mg) / small_symbiont_count
merged_host_et_zoox$protein_SSC_norm_zoox<- merged_host_et_zoox$protein_SSC_norm_zoox / merged_host_et_zoox$small_symbiont_count

# Converting mg/sa --> ng/sa 
merged_host_et_zoox$protein_SSC_norm_zoox <- merged_host_et_zoox$protein_SSC_norm_zoox * (1e+06)
```

### Graphing: Small Symbiont Count Normalized Zoox Protein  vs _____

## SSC Zoox protein vs treatments 
```{r}
#24 Protein per coral of zoox vs treatments 
gg_base_24 <- ggplot(data = merged_host_et_zoox, aes(x = treatment, y = protein_SSC_norm_zoox, group = treatment))
violin_24 <- gg_base_24 + geom_violin()
violin_24 + geom_boxplot(width = 0.1) + labs(title = "Zoox SSC norm protein by treatment") + ylim(0,70) + ylab("Zoox: ng protein/SSC")
```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(treatment) %>%
  get_summary_stats(protein_SSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "treatment", y = "protein_SSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(treatment) %>%
  identify_outliers(protein_SSC_norm_zoox) 

# Check Normailty: Build the linear model
model_8  <- lm(protein_SSC_norm_zoox ~ treatment, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_8))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_8))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(treatment) %>%
  shapiro_test(protein_SSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_zoox", facet.by = "treatment")

# Homogenietey of variance assumption 
plot(model_8, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_zoox ~ treatment)
res.aov

```




## SSC Zoox Protein vs Colony 
```{r}
#25 Protein per coral of Zoox vs colony 
gg_base_25 <- ggplot(data = merged_host_et_zoox, aes(x = colony, y = protein_SSC_norm_zoox, group = colony))
violin_25 <- gg_base_25 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_25 + geom_boxplot(width = 0.1) + labs(title = "Zoox SSC norm protein by colony") + ylim(0,100) + ylab("Zoox: ng protein/SSC")

```

```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(colony) %>%
  get_summary_stats(protein_SSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "colony", y = "protein_SSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(colony) %>%
  identify_outliers(protein_SSC_norm_zoox) 

# Check Normailty: Build the linear model
model_4  <- lm(protein_SSC_norm_zoox ~ colony, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_4))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_4))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(colony) %>%
  shapiro_test(protein_SSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_zoox", facet.by = "colony")

# Homogenietey of variance assumption 
plot(model_4, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_zoox ~ colony)
res.aov

```




## SSC Zoox Protein vs Tank 
```{r}
#26 protein per coral of Zooxt vs tank 
gg_base_26 <- ggplot(data = merged_host_et_zoox, aes(x = tank, y = protein_SSC_norm_zoox, group = tank))
violin_26 <- gg_base_26 + geom_violin() + scale_x_continuous(breaks=c(1:12))
violin_26 + geom_boxplot(width = 0.1) + labs(title = "Zoox SSC norm protein by tank") + ylim(0,30) + ylab("Zoox: ng protein/SSC")

```


```{r, Checking for Outliers}
# Summary Statistics: Before removing outliers 
merged_host_et_zoox %>%
  group_by(tank) %>%
  get_summary_stats(protein_SSC_norm_zoox, type = "mean_sd")
# Visualization 
ggboxplot(merged_host_et_zoox, x = "tank", y = "protein_SSC_norm_zoox")

# Check Assumptions: Outliers --> there are 2 extreme outliers 
merged_host_et_zoox %>% 
  group_by(tank) %>%
  identify_outliers(protein_SSC_norm_zoox) 

# Check Normailty: Build the linear model
model_12  <- lm(protein_SSC_norm_zoox ~ tank, data = merged_host_et_zoox)
  # Create a QQ plot of residuals
ggqqplot(residuals(model_12))
  # Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model_12))  # we had a p < 0.05, which means that the data significantly deviates from a normal distribution 

#Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.
merged_host_et_zoox %>%
  group_by(tank) %>%
  shapiro_test(protein_SSC_norm_zoox) # some colonies are <0.05, which means they are not normally distributed 

# Checking normality of each colony 
ggqqplot(merged_host_et_zoox, "protein_SSC_norm_zoox", facet.by = "tank")

# Homogenietey of variance assumption 
plot(model_12, 1) 

#Computation 
res.aov <- merged_host_et_zoox %>% anova_test(protein_SSC_norm_zoox ~ tank)
res.aov

```

*** 




























